---
title: "Homework 1"
author: "Cong Zhang"
date: 2020-09-19
output: github_document
---

This is my solution to Homework 1.

```{r message = FALSE}
library(tidyverse)
```


## Problem 1

Create a data frame with the required elements.

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

Take the mean of numbers and logical but not character or factor. 

```{r try_numeric, eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Convert the logical vector.

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


## Problem 2

The code chunk below loads the penguins dataset and generates a plot.

Load the penguins dataset.

```{r penguins_df}
data("penguins", package = "palmerpenguins")
```


Write description of the dataset.

* This dataset has following variables: `r ls(penguins)`.

* Here are some values of important variables:

  * Excluding missing values, the range of variable bill_length_mm is (`r min(pull(penguins, bill_length_mm), na.rm = TRUE)`,`r max(pull(penguins, bill_length_mm), na.rm = TRUE)`) and the median is `r median(pull(penguins, bill_length_mm), na.rm = TRUE)`.
  
  * Excluding missing values, the range of variable flipper_length_mm is (`r min(pull(penguins, flipper_length_mm), na.rm = TRUE)`,`r max(pull(penguins, flipper_length_mm), na.rm = TRUE)`) and the median is `r median(pull(penguins, flipper_length_mm), na.rm = TRUE)`.
  
  * The penguins belong to following species: `r levels(pull(penguins, species))`.
  
* This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* Excluding missing values, the mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.


Generate a scatterplot.

```{r plot_penguins}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species )) + geom_point()
```

Export the scatterplot.

```{r export_plot}
ggsave("penguins_scatterplot.pdf")
```
